Supplement 3

### 2020-09-10 paper/paper.Rmd
minor clean ups to text

Imputing data might feel wrong, as we are 'making up data'. The truth
is, we (generally) can never know what the missing values were. The goal
of imputing data is to make the best possible inference from the data.
We recommend data is imputed, with a few caveats. Consider removing
variables with a high proportion of missing data (e.g., variables with
the majority or more missing than not). With respect to a 'rule of
thumb' for when data should be imputed, we deliberately do not suggest
any specific threshold (e.g., impute values when >5% of data are
missing otherwise delete rows with <5% missing) and caution against
such practice. Rather, we recommend values should generally be imputed. 
We recommend avoiding imputation methods that impute the same value,
such as the mean or median, and instead suggest using imputation
methods such as: linear regression, k-nearest neighbours, or expectation
maximisation. Missing values can occur in the both the predictors (the "independent variables") 
and response variable (the "dependent variables"). Care should be taken 
when imputing data, as typically only predictors should be imputed. 
For discussion on imputing the response value, see ... [@refs]. **(note: take a look again)**

>>>>

Imputing data might feel wrong, as we are 'making up data'. The truth
is, we can (generally) never know what the missing values were. The goal
of imputing data is to make the best possible inference from the data.
We recommend data is imputed, with a few caveats. Consider removing
variables with a high proportion of missing data (e.g., variables with
the majority or more missing than not). We deliberately do not suggest a 'rule of
thumb' for the amount of missingness that should be imputed, and caution against
looking for a specific threshold. Rather, we recommend: values should generally be imputed, avoiding methods imputing the same value (such as the mean or median), and suggest using imputation methods such as: linear regression, k-nearest neighbours, or expectation
maximisation.

Missing values can occur in the both the predictors (the "independent variables") 
and response variable (the "dependent variables"). Care should be taken 
when imputing data, as typically only predictors should be imputed. 
For discussion on imputing the response value, see ... [@refs]. **(note: take a look again)**

### 2020-09-10 paper/supplement-2.Rmd
minor clean ups to text

Football related articles published in 2019 were studied. Three major
sports medicine databases were searched on May 20, 2020, using key terms and limits. 
The databases were: SPORTDiscus, Embase and Cinahl. A
list of the search terms and complete search statements are provided in
Table \@ref(tab:search-table).

@@

search_table %>% 
  gt() %>% 
  cols_width(
    vars(Sportdiscus, Cinahl) ~ px(240),
    vars(Embase) ~ px(300)
    )
```

>>>>

Football related articles published in 2019 were studied. Three major
sports medicine databases were searched on May 20, 2020, using key terms and limits. 
The databases were: SPORTDiscus, Embase and Cinahl. A
list of the search terms and complete search statements are provided in
Table 1 below

@@

search_table %>%
  gt() %>%
  cols_width(
    vars(Sportdiscus) ~ px(320),
    vars(Cinahl) ~ px(280),
    vars(Embase) ~ px(280)
    )

_Table 1. Caption here._

### 2020-09-10 paper/supplement-3.Rmd
minor clean ups to text

```{r}
library(tidyverse)
library(fitzRoy)
library(mice)
library(naniar)

# Aim of this section:
# Simulate data from a real data set, insert missing
# Mini study: predicting super coach scores

d = fitzRoy::get_afltables_stats(start_date = "2020-01-01", end_date = "2020-09-04")

@@

df <- fitzRoy::get_footywire_stats(10286:10290) # Get the fantasy scores
View(df)
df #%>% View("footywire dataset")

# Simulate data from summarises of the above dataset
rnorm(n = 100, # N is the amount of data points being generated
      mean = 5,
      sd = 2)
sample.int(100, # numbers between 1 and 100
           10) # observations
rpois(n = 100,
      lambda = 5)

# Generate the y-variable
fit <- lm(AF ~ K + HB, data = df)
summary(fit)
data %>% mutate(fanasty_score = 4.106*Kicks + 2.175*Handballs)

# Completed dataset
# Drop a team
No_Richmond <- df %>% filter(Team!="Richmond")
sort(unique(No_Richmond$Team))
sort(unique(df$Team))

# Impute missing values
df_first_try <- mice::ampute(data = df[,10:43])
df_first_try <- df_first_try$amp

# Examples of presenting of missing values
naniar::vis_miss(df_first_try)
naniar::vis_miss(df_first_try)
naniar::gg_miss_fct(x = riskfactors, fct = marital)

>>>>

```{r library}
library(tidyverse)
library(fitzRoy)
library(mice)
library(naniar)
```

```{r}
# Aim of this section:
# Simulate data from a real data set, insert missing
# Mini study: predicting super coach scores

d <- get_afltables_stats(start_date = "2020-01-01", 
                         end_date = "2020-09-04")

@@

df <- get_footywire_stats(10286:10290) # Get the fantasy scores

# View(df)
df #%>% View("footywire dataset")
```

```{r}
# Simulate data from summarises of the above dataset
rnorm(n = 100, # N is the amount of data points being generated
      mean = 5,
      sd = 2)
sample.int(100, # numbers between 1 and 100
           10) # observations
rpois(n = 100,
      lambda = 5)
```

```{r}
# Generate the y-variable
fit <- lm(AF ~ K + HB, data = df)
summary(fit)
data %>% mutate(fanasty_score = 4.106*Kicks + 2.175*Handballs)
```

```{r}
# Completed dataset
# Drop a team
No_Richmond <- df %>% filter(Team!="Richmond")
sort(unique(No_Richmond$Team))
sort(unique(df$Team))
```

```{r}
# Impute missing values
df_first_try <- mice::ampute(data = df[,10:43])
df_first_try <- df_first_try$amp
```

```{r}
# Examples of presenting of missing values
naniar::vis_miss(df_first_try)
naniar::vis_miss(df_first_try)
naniar::gg_miss_fct(x = riskfactors, fct = marital)
